### 2018-03-12 Docs/FAQ/faq.tex

   The environment variable {\tt BOXLIB\_HOME} needs to be the full path
   to the {\tt BoxLib} directory.  You cannot use `{\tt $\sim$}' as a shortcut
   for your home directory.

\item {\em {\tt make} issues an error like:
       {\small
       \begin{verbatim}
       .../BoxLib/Tools/F_mk/GMakeMPI.mak:40: Extraneous text after `else' directive
       .../BoxLib/Tools/F_mk/GMakeMPI.mak:47: *** only one `else' per conditional.  Stop
      \end{verbatim}
      }
      }

@@

\boxlib\ can intercept floating point exceptions and provide a helpful
backtrace that shows you where they were generated.  See \S
\ref{ch:makefiles:special}.

@@

 One implementation of this can be found in {\tt
   BoxLib/Tools/Postprocessing/F\_Src/tutorial/fwrite2d.f90}.  This reads in
 the plotfile data using the {\tt plotfile\_module} that the {\tt
   data\_processing} routines rely on, but then builds a multifab
   and writes the data out to a plotfile using the BoxLib write
   routines.

>>>>

   The environment variable {\tt AMREX\_HOME} needs to be the full path
   to the {\tt amrex/} directory.  You cannot use `{\tt $\sim$}' as a shortcut
   for your home directory.

\item {\em {\tt make} issues an error like:
       {\small
       \begin{verbatim}
       .../amrex/Tools/F_mk/GMakeMPI.mak:40: Extraneous text after `else' directive
       .../amrex/Tools/F_mk/GMakeMPI.mak:47: *** only one `else' per conditional.  Stop
      \end{verbatim}
      }
      }

@@

\amrex\ can intercept floating point exceptions and provide a helpful
backtrace that shows you where they were generated.  See \S
\ref{ch:makefiles:special}.

@@

 One implementation of this can be found in {\tt
   amrex/Tools/Postprocessing/F\_Src/tutorial/fwrite2d.f90}.  This reads in
 the plotfile data using the {\tt plotfile\_module} that the {\tt
   data\_processing} routines rely on, but then builds a multifab
   and writes the data out to a plotfile using the \amrex\ write
   routines.
